---
title: "additional_sim_analysis_code"
output: html_document
---

# OLD

### Matrix of different outcome values / metrics across all districts (conditional on solver constraints and objective functions)
```{r message=FALSE, warning=FALSE}
compute_matrix_of_outcomes <-
  function(df,
           curr_obj_fcn,
           curr_travel,
           curr_school_size,
           curr_comm_cohesion,
           opt_cats,
           outcome_cats,
           curr_metric,
           curr_value,
           key_string) {
    M <- matrix(nrow = length(opt_cats), ncol = length(outcome_cats))
    row_names <- c()
    for (i in 1:length(opt_cats)) {
      c1 <- opt_cats[i]
      row_names <- c(row_names, c1)
      curr_df <- df %>% filter(
        travel_time_threshold == curr_travel,
        school_size_threshold == curr_school_size,
        community_cohesion_threshold == curr_comm_cohesion,
        objective_function == curr_obj_fcn,
        cat_optimizing_for == c1
      )
      curr_df[is.na(curr_df)] <- 0
      col_names <- c()
      for (j in 1:length(outcome_cats)) {
        c2 <- outcome_cats[j]
        col_names <- c(col_names, c2)
        if (key_string != '') {
          key = paste(c2, curr_metric, curr_value, key_string, sep = "_")
        }
        else {
          key = paste(c2, curr_metric, curr_value, sep = "_")
        }
        
        M[i, j] <-
          weighted.mean(curr_df[[key]], curr_df$total_enrollment_in_district, na.rm = T)
      }
    }
    rownames(M) <- opt_cats
    colnames(M) <- outcome_cats
    print(M)
    longData <- melt(M)
    p <- ggplot(longData, aes(x = X1, y = X2)) +
      geom_raster(aes(fill = value)) +
      geom_text(aes(label = round(value, 4))) +
      scale_fill_gradient2(low = "green", mid="white", high = "red", midpoint=0) +
      labs(
        x = "Category optimizing for",
        y = sprintf(
          "%s perc. change in %s for category (across districts)",
          curr_metric,
          curr_value
        ),
        title =
          sprintf(
            "Travel threshold: %s, School size threshold: %s, Cohesion: %s, Obj. fcn: %s",
            curr_travel,
            curr_school_size,
            curr_comm_cohesion,
            curr_obj_fcn
          )
      ) +
      theme_bw() + theme(
        axis.text.x = element_text(
          size = 9,
          angle = 0,
          vjust = 0.3
        ),
        axis.text.y = element_text(size = 9),
        plot.title = element_text(size = 11)
      )
    
    return (p)
  }

```

#### H4: Seeking to minimize segregation for one category of students may lead to disproportionate increases in segregation for other categories of students
```{r message=FALSE, warning=FALSE}
df_richmond <- df %>% filter(district_id == 5103240)
df_henrico = df %>% filter(district_id == 5101890)

curr_value <- 'segregation'
curr_metric <- 'median'
curr_key <- 'change'
opt_cats <-  c('black', 'hisp', 'frl', 'ell', 'white')
outcome_cats <-  c('black', 'hisp', 'frl', 'ell', "white")

p1 <- compute_matrix_of_outcomes(
  df,
  'min_max',
  0.5,
  0.2,
  0,
  opt_cats,
  outcome_cats,
  curr_metric,
  curr_value,
  curr_key
)

curr_value <- 'rezoned'
curr_metric <- 'percent'
curr_key <- ''
opt_cats <-  c('black', 'hisp', 'frl', 'ell', 'white')
outcome_cats <-  c('black', 'hisp', 'frl', 'ell', 'white')

p2 <- compute_matrix_of_outcomes(
  df_richmond,
  'min_max',
  0.5,
  0.2,
  0.5,
  opt_cats,
  outcome_cats,
  curr_metric,
  curr_value,
  curr_key
)

curr_value <- 'travel_time'
curr_metric <- 'total'
curr_key <- 'change'
opt_cats <-  c('black', 'hisp', 'frl', 'ell', 'white')
outcome_cats <-  c('black', 'hisp', 'frl', 'ell', 'white')

p3 <- compute_matrix_of_outcomes(
  df,
  'min_total',
  0.5,
  0.2,
  0,
  opt_cats,
  outcome_cats,
  curr_metric,
  curr_value,
  curr_key
)



```

### Histograms of different outcome values / metrics across all districts (conditional on solver constraints and objective functions)
```{r message=FALSE, warning=FALSE}
compute_histograms_of_outcomes <- function(curr_cats,
                                           curr_obj_fcns,
                                           curr_travel,
                                           curr_school_size,
                                           curr_comm_cohesion,
                                           curr_metrics,
                                           curr_values,
                                           opt_cat,
                                           key_string) {
  num_rows = length(travel_thresholds) * length(size_thresholds) * length(obj_fcns) * length(curr_comm_cohesion)
  num_cols = length(metrics) * length(values)
  par(mfrow = c(num_rows, num_cols))
  for (c in curr_cats) {
    for (o in curr_obj_fcns) {
      for (t in curr_travel) {
        for (s in curr_school_size) {
          for (z in curr_comm_cohesion) {
            curr_df = df %>% filter(
              travel_time_threshold == t,
              school_size_threshold == s,
              objective_function == o,
              cat_optimizing_for == opt_cat,
              community_cohesion_threshold == z
            )
            curr_df[is.na(curr_df)] <- 0
            for (m in curr_metrics) {
              for (v in curr_values) {
                if (key_string != '') {
                  key = paste(c, m, v, key_string, sep = "_")
                }
                else {
                  key = paste(c, m, v, sep = "_")
                }
                plot <-
                  ggplot(curr_df, aes(x = eval(parse(
                    text = key
                  )))) +
                  geom_histogram(binwidth = .05) +
                  xlim(c(-1, 1)) +
                  ggtitle(paste(
                    paste('opt_for=', opt_cat),
                    paste('obj_fcn=', o),
                    paste('travel_increase=', t),
                    paste('size_increase=', s),
                    paste('comm_cohesion=', z),
                    paste('weighted_average=',
                          weighted.mean(curr_df[[key]], curr_df$total_enrollment_in_district, na.rm = T)),
                    sep = ", "
                  )) +
                  xlab(paste(key)) +
                  theme(text = element_text(size = 7))
                print(plot)
              }
            }
            
          }
        }
      }
    }
  }
}
```

#### 

##### Segregation values
```{r message=FALSE, warning=FALSE}
curr_obj_fcns <- c('min_total', 'min_max')
curr_travel <- c(0.5)
curr_school_size <- c(0.1)
curr_comm_cohesion <- c(0.5)
curr_values <- c('segregation')
curr_metrics <- c('total')
curr_cats <- ('black')
compute_histograms_of_outcomes(curr_cats,
                               curr_obj_fcns,
                               curr_travel,
                               curr_school_size,
                               curr_comm_cohesion,
                               curr_metrics,
                               curr_values,
                               'black',
                               'change')
```

##### Computing matrix visualization
```{r message=FALSE, warning=FALSE}
compute_matrix_of_outcomes_best_configs <-
  function(df,
           outcome_cats,
           outcome_string) {
    
    M <-
      matrix(nrow = length(outcome_cats),
             ncol = length(outcome_cats))
    row_names <- c()
    for (i in 1:length(outcome_cats)) {
      c1 <- outcome_cats[i]
      row_names <- c(row_names, c1)
      curr_df <- df %>% filter(cat_best_for == c1)
      curr_df[is.na(curr_df)] <- 0
      for (j in 1:length(outcome_cats)) {
        c2 <- outcome_cats[j]
        col_name <- paste(c2, outcome_string, sep = "_")
        
        if (outcome_string == 'all_xexposure_prob') {
          M[i, j] <- mean(parse_and_agg_list_entries_xexposure(curr_df, col_name), na.rm=T)
        }
        else if (outcome_string == 'total_travel_time_for_rezoned_change') {
          total_diff <- sum(curr_df[[paste(c2, "total_travel_time_for_rezoned_diff", sep="_")]], na.rm=T)
          total_orig <- sum(curr_df[[paste(c2, "total_travel_time_for_rezoned", sep="_")]], na.rm=T)
          M[i, j] <- total_diff / total_orig
        }
        else if (outcome_string == 'percent_rezoned'){
          M[i, j] <- sum(curr_df[[paste(c2, 'num_rezoned', sep = "_")]]) / sum(curr_df[[paste(c2, 'num_total', sep = "_")]])
        }
        else if (outcome_string == 'total_xexposure_num_diff') {
          M[i, j] <- sum(curr_df[[col_name]])
        }
        
      }
    }
    rownames(M) <- outcome_cats
    colnames(M) <- outcome_cats
    longData <- melt(M)
    low_color <- 'red'
    high_color <- 'green'
    if (str_contains(outcome_string, 'percent_rezoned') ||
        str_contains(outcome_string, 'travel_time') ||
        str_contains(outcome_string, 'gini')) {
      low_color <- 'green'
      high_color <- 'red'
    }
    p <- ggplot(longData, aes(x = X1, y = X2)) +
      geom_raster(aes(fill = value), show.legend = FALSE) +
      geom_text(aes(label = round(value, 4))) +
      scale_fill_gradient2(
        low = low_color,
        mid = "white",
        high = high_color,
        midpoint = 0
      ) +
      labs(x = "Best increase in p(cross_exposure) for category:",
           y = sprintf("Resulting %s for category: ", outcome_string),) +
      theme_bw() + theme(
        axis.text.x = element_text(
          size = 9,
          angle = 0,
          vjust = 0.3
        ),
        axis.text.y = element_text(size = 9),
        plot.title = element_text(size = 11)
      )
    
    return (p)
  }
```
